Analysis of the properties of probabilistic models in learning problems with an expert\thanks{Grants or other notes about the article that should go on the front page should be placed here. General acknowledgments should be placed at the end of the article.}

### 2020-12-30 paper/Bazarova2020Springer/template.tex
add springer

\documentclass[12pt, twoside]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\usepackage{amsthm}
\usepackage{a4wide}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{mathrsfs}
\usepackage{euscript}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{color}
\usepackage{bm}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage[toc,page]{appendix}
\usepackage{comment}
\usepackage{rotating}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\newtheorem{definition}{Definition}[section]
\numberwithin{equation}{section}
\newcommand*{\No}{No.}

\begin{document}

\title{\bf Analysis of the properties of probabilistic models in learning problems with an expert}
\date{}
\author{}
\maketitle

\begin{center}
\bf
A.\,V.~Grabovoy\footnote{Moscow Institute of Physics and Technology, grabovoy.av@phystech.edu}, 
A.\,I. Bazarova\footnote{Moscow Institute of Physics and Technology, bazarova.ai@phystech.edu}, 
V.\,V.~Strijov\footnote{Moscow Institute of Physics and Technology, strijov@phystech.edu}

\end{center}
{\centering\begin{quote}
\textbf{Abstract:} This paper is devoted to the construction of interpretable models in machine learning. 
It solves the problem of approximating a given set of figures on a contour image.
Assumptions are introduced that the figures are curves of the second order.
When approximating figures, information about the type, location and form of curves, as well as the set of their possible transformations, is used.
Such information is called \textit{expert}, and the machine learning method based on expert information is called \textit {expert learning}.
It is assumed that the set of shapes is approximated by a set of \textit {local models}.
Each local model, based on expert information, approximates one shape in the contour image.
To build models, it is proposed to map second-order curves into a feature space where each local model is a linear model.
Thus, higher-order curves are recognized using the composition of linear models.
As an applied problem, the problem of approximating the iris of the eye on a contour image is considered.

\smallskip
\textbf{Keywords}: mixture of experts, expert learning, linear models, interpretabe models
\smallskip
%\textbf{DOI}: 00.00000/00000000000000
\end{quote}
}

\section {Introduction}
Interpretable model building in machine learning~\cite{Ribeiro2016} is one of the key challenges.
Modern solutions of the image classification problem based on deep learning networks ResNet, VGG, Intercept~\cite{Kaiming2015} are poorly interpreted models.
The papers~\cite{Han2020, Xingjun2019, Akhtar2018} show that deep learning networks are sensitive even to small noise in the data, which is due to their uninterpretability.

@@

This paper solves the problem of approximating second-order curves on a contour image. Second-order curves are selected for analysis, since they are easily described by linear models. In this case, these figures need to be restored in such applied problems as the problem of recognizing the iris of the eye~\cite{Matveev2010, Matveev2014, Bowyer2010}, the problem of describing the particle track in the hadron collider~\cite{Dalila2018}. Expert information about a second-order curve allows you to map points on a plane into a new feature description, where each curve is approximated by one linear model. A model that approximates one curve is called a \textit {local model}. To approximate the entire contour image, it is required to approximate several second-order curves using several local models. In this paper, the following restrictions on images are introduced:
\begin{enumerate}
	\item[1)] the image consists only of second-order curves;
	\item[2)] the image is approximated by a small number of second-order curves;
	\item[3)] the number and type of curves in the image is known.
\end{enumerate}

\begin{figure}[h!]
     \centering
     \includegraphics[width=\textwidth]{figures/explanation}
\caption {Example: a) expert information of the first expert; b) baseline data; c) expert information of the second expert.}
    \label{intro:fig2}
\end{figure}

@@

\begin{figure}[h!]
     \centering
     \begin{subfigure}[b]{0.3\textwidth}
         \centering
         \includegraphics[width=\textwidth]{figures/real_image}
         \caption{}
         \label{intro:fig1:real}
     \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
         \centering
         \includegraphics[width=\textwidth]{figures/outline_image}
         \caption{}
         \label{intro:fig1:outer}
     \end{subfigure}
\caption{An example of the image of the iris of the eye and its outline representation: a) the image of the iris of the eye; b) contour image of the iris and approximating the given image of the circumferences.}    \label{intro:fig1}
\end{figure}

@@

\section{Statement of the problem of finding the parameters of the second-order curves in the image}
Binary image is set:
$$ \mathbf{M} \in \{0, 1 \}^{m_1\times m_2},$$
where 1 corresponds to the black point of the image, and 0 corresponds to the white point of the background.
From the image $\mathbf {M} $, a sample$ \mathbf{C}$ is constructed, the elements of which are the coordinates $(x_i, y_i)$ of black points: $$\mathbf {C} \in \mathbb {R}^{N \times 2}. $$
The expert assumes that the image consists of a second-order curve~$\Omega$.
Let for a set of points $\mathbf {C} \in \mathbb {R}^{N \times 2} $ that form a curve $\Omega, $ expert information about the figure $E(\Omega) $is given.
The set $E (\Omega)$ consists of the shape $\Omega$ expected by the expert and the set of its admissible transformations. Based on the expert description, let us introduce mappings into a new problem for approximation:
\begin{equation}\label{eq1}
	K_{x}\bigl(E(\Omega)\bigr): \mathbb{R}^{2} \rightarrow \mathbb{R}^{n}, \quad K_{y}\bigl(E(\Omega)\bigr): \mathbb{R}^{2} \rightarrow \mathbb{R},
\end{equation} 
where~$K_{x}$ mapping objects to the attribute description of objects,~$n$is the number of features, and~$K_ {y}$ is a mapping to a target variable for an object. Applying the mappings~$K_ {x}, K_{y}$for the sample~$\mathbf {C}$ element by element we obtain:
\begin{equation}
\label{eq2}
	K_{x}\bigl(E(\Omega\bigr), \mathbf{c}) = \mathbf{x}, \quad  K_{y}\bigl(E(\Omega), \mathbf{c}\bigr) = y,
\end{equation}
where~$\mathbf{c} = (x_i, y_i)$ is a sample point $\mathbf{C}$.

@@

\section{Building an attribute description of figures }
\paragraph{ Unified space for second-order curves.} An arbitrary second-order curve, the main axis of which is not parallel to the ordinate axis, is given by the following expression:
\[
\label{st:coef}
x^2 = B'xy+C'y^2+D'x+E'y+F',
\]
where the coefficients $B ', C'$ are subject to restrictions that depend on the type of the curve. The expression~\eqref{eq2} takes the following form:
\[
\label{st:K_map}
K_x\bigr(\mathbf{c}_i\bigr)=\left[x_iy_i, y_i^2, x_i, y_i, 1\right], \quad K_y\bigr(\mathbf{c}_i\bigr)=x_i^2,
\]
whence we obtain the linear regression problem for recovering the parameters~$ B ', C', D ', E', F '$ from the selected sample.

@@

\section{Composition of figures }
To construct a composition of figures, we will use the expression~\eqref{9}, which takes the following form:
\begin{equation} 
\label{statment:optim:task}
\begin{aligned}
\mathcal{L} = \sum\limits_{\mathbf{c} \in \mathbf{C}} \sum\limits_{k = 1}^{K} \pi_k(\mathbf{c}, \mathbf{V})\left(K^{k}_y\bigr(\mathbf{c}\bigr) - \mathbf{w}_k^{\mathsf{T}}K^{k}_x\bigr(\mathbf{c}\bigr)\right)^2 + R\bigl(\mathbf{V}, \mathbf{W}, E(\Omega)\bigr) \rightarrow \min_{\mathbf{V}, \mathbf{W}},
\end{aligned}
\end{equation} 
where~$K^{k}_x, K^{k}_y$ expert representation of the~$k$-th expert. Assuming that all curves in the image are described by one attribute description $\mathbf {x} =K^{1}_x\bigr(\mathbf{c}\bigr)=\cdots=K^{K}_x\bigr(\mathbf{c}\bigr), x= K^{1}_y\bigr(\mathbf{c}\bigr)=\cdots=K^{K}_y\bigr(\mathbf{c}\bigr),$ we get the following optimization problem:
\begin{equation} 
\label{statment:optim:task:simp}
\begin{aligned}
\mathcal{L} = \sum\limits_{\left(\mathbf{x}, y\right) \in \mathfrak{D}} \sum\limits_{k = 1}^{K} \pi_k(\mathbf{x}, \mathbf{V})\left(y - \mathbf{w}_k^{\mathsf{T}}\mathbf{x}\right)^2 + R\bigl(\mathbf{V}, \mathbf{W}, E(\Omega)\bigr) \rightarrow \min_{\mathbf{V}, \mathbf{W}},
\end{aligned}
\end{equation}

@@

\section{ Computing experiment }
A computational experiment was carried out to analyze the quality of models of second-order curves in the image. The experiment is divided into several parts. The first part is an experiment with several circumferences in the image. The second part analyzes the convergence of the method depending on the noise level in the data and on the specified expert information. In the third part, an experiment is conducted to approximate the iris of the eye.

\subsection{ Experiment with circumstances }
\begin{figure}[h!]
\begin{minipage}{.32\textwidth}
      \includegraphics[width =  \textwidth]{figures/900.eps}
\end{minipage}
\begin{minipage}{.32\textwidth}
\hspace{2mm}
      \includegraphics[width =  0.9\textwidth]{figures/901.eps}
\end{minipage}
\begin{minipage}{.32\textwidth}
\hspace{-2.3mm}
      \includegraphics[width =  0.935\textwidth]{figures/902.eps}
\end{minipage}
\caption{Multi-model depending on different prior assumptions and noise level. From left to right: circumferences without noise; noise in the radius of the circle; noise in the radius of a circle as well as arbitrary points throughout the image.}
\label{ce:fig3}
\end{figure}

\begin{figure}[h]
\begin{minipage}{.32\textwidth}
\hspace{-3mm}
      \includegraphics[width = 1.05\textwidth]{figures/900noise.eps}
\end{minipage}
\begin{minipage}{.32\textwidth}
\hspace{-2.1mm}
      \includegraphics[width = \textwidth]{figures/901noise.eps}
\end{minipage}
\begin{minipage}{.32\textwidth}
\hspace{-2mm}
      \includegraphics[width = 0.95\textwidth]{figures/902noise.eps}
\end{minipage}
\caption{Dependence of the parameters  $r$, $x_0$ and $y_0$ on the iteration number for different prior distributions. From left to right: circumferences without noise; noise in the radius of the circle; noise in the radius of a circle as well as arbitrary points throughout the image.}
\label{ce:fig4}
\end{figure}

@@

\subsection{ Experiment with different noise levels and variance of the prior distribution }
\begin{figure}[h!t]\center
\includegraphics[width=0.8\textwidth]{figures/beta_gamma}
\caption{ The result of the approximation for data with different noise levels~$\beta$ and on the variance of the prior distribution~$\gamma$}
\label{ce:fig6}
\end{figure}

@@

\subsection{Iris approximations }
\begin{figure}
     \centering
     \begin{subfigure}[b]{0.3\textwidth}
         \centering
         \includegraphics[width=\textwidth]{figures/not_prior_real_example}
         \caption{}
     \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
         \centering
         \includegraphics[width=\textwidth]{figures/prior_real_example}
         \caption{}
     \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
         \centering
         \includegraphics[width=\textwidth]{figures/prior_regular_real_example}
         \caption{}
     \end{subfigure}
     \caption{ Visualization of the approximation of the iris: a) if the $ R_0 $ regularizer is specified; b) if the $ R_1 $ regularizer is specified; b) if the $ R_2 $ regularizer is specified.}
    \label{ce:fig6}
\end{figure}

\begin{figure}
     \centering
     \includegraphics[width=\textwidth]{figures/experiment_real_not_prior}\\

     \caption{Visualization of the multi-model convergence process in the case of a regularizer~$R_0$}
    \label{ce:fig7}
\end{figure}

\begin{figure}
     \centering
     \includegraphics[width=\textwidth]{figures/experiment_real_prior}
     \caption{Visualization of the multi-model convergence process in the case of a regularizer~$R_1$}
    \label{ce:fig8}
\end{figure}

\begin{figure}
     \centering
     \includegraphics[width=\textwidth]{figures/experiment_real_regular}
     \caption{Visualization of the multi-model convergence process in the case of a regularizer~$R_2$}
    \label{ce:fig9}
\end{figure}

@@

\section{Conclusion}
The paper proposes a method for constructing interpretable machine learning models based on expert information. The problem of approximation of the second-order curves: parabola, hyperbola, ellipse is considered as a problem. Approximation of curves of the second order is applied in the problem of approximation of the iris of the eye.

@@

\begin{thebibliography}{99}
\bibitem{Ribeiro2016}
	\textit{Marco Tulio Ribeiro, Sameer Singh, Carlos Guestrin} "Why Should I Trust You?": Explaining the Predictions of Any Classifier // Proceedings of the 22nd ACM SIGKDD International Conference on Knowledge Discovery and Data Mining PP. 1135--1144. 2016

\bibitem{Tianqi2016}
	\textit{Chen Tianqi, Guestrin Carlos} XGBoost: A Scalable Tree Boosting System~// KDD ’16 Proceedings of the 22nd ACM SIGKDD International Conference on Knowledge Discovery and Data Mining. 2016.

\bibitem{Ishwaran2012}
	\textit{Chen Xi, Ishwaran Hemant} Random Forests for Genomic Data Analysis~// Genomics. 2012. Issues. 99, No 6. pp. 323--329.

\bibitem{Yuksel2012}
	\textit{Yuksel Seniha Esen, Wilson Joseph N., Gader Paul D} Twenty Years of Mixture of Experts~// IEEE Transactions on Neural Networks and Learning Systems. 2012. Issues. 23, No 8. pp. 1177--1193.

\bibitem{Cao2003}
	\textit{L.~Cao} Support vector machines experts for time series forecasting~// Neurocomputing, vol. 51, pp. 321–339, Apr. 2003.

\bibitem{Dempster1977}
	\textit{A. P. Dempster, N. M. Laird and D. B. Rubin} Maximum Likelihood from Incomplete Data via the EM Algorithm~// Journal of the Royal Statistical Society. Series B (Methodological), Vol. 39, No. 1 pp. 1-38, 1977.

\bibitem{Yumlu2003}
	\textit{M.\,S.~Yumlu, F.\,S.~Gurgen,  N.~Okay} Financial time series prediction using mixture of experts~// in Proc. 18th Int. Symp. Comput. Inf. Sci., 2003, pp. 553--560.

\bibitem{Cheung1995}
	\textit{Y.~M.~Cheung, W.~M.~Leung, and L. Xu} Application of mixture of experts model to financial time series forecasting~// in Proc. Int. Conf. Neural Netw. Signal Process., 1995, pp. 1--4.

\bibitem{Weigend2000}
	\textit{A. S. Weigend, S. Shi} Predicting daily probability distributions of S\&P500 returns~// J. Forecast., vol. 19, no. 4, pp. 375--392, 2000.

\bibitem{Ebrahimpour2009}
	\textit{R. Ebrahimpour, M. R. Moradian, A. Esmkhani, F. M. Jafarlou} Recognition of Persian handwritten digits using characterization loci and mixture of experts~// J. Digital Content Technol. Appl., vol. 3, no. 3, pp. 42–46, 2009.

\bibitem{Estabrooks2001}
	\textit{A.~Estabrooks, N.~Japkowicz} A mixture-of-experts framework for text classification~//in Proc. Workshop Comput. Natural Lang. Learn., Assoc. Comput. Linguist., 2001, pp. 1--8.

\bibitem{Mossavat2010}
	\textit{S. Mossavat, O. Amft, B. de Vries, P. Petkov, W. Kleijn} A Bayesian hierarchical mixture of experts approach to estimate speech quality~// in Proc. 2nd Int. Workshop Qual. Multimedia Exper., pp. 200--205., 2010

\bibitem{Sminchisescu2007}
	\textit{C. Sminchisescu, A. Kanaujia, and D. Metaxas} B M3 E: Discrimina- tive density propagation for visual tracking~// IEEE Trans. Pattern Anal. Mach. Intell., vol. 29, no. 11, pp. 2030–2044, 2007.

\bibitem{Matveev2010}
	\textit{I. Matveev} Detection of iris in image by interrelated maxima of brightness gradient projections~// Appl.Comput. Math. 9 (2), 252–257, 2010.

\bibitem{Matveev2014}
	\textit{I. Matveev, I. Simonenko}. Detecting precise iris boundaries by circular shortest path method~// Pattern Recognition and Image Analysis. 24. 304-309. 2014.

\bibitem{Bowyer2010}
	\textit{K. Bowyer, K. Hollingsworth, P. Flynn} A Survey of Iris Biometrics Research: 2008–2010.

\bibitem{Peng1996}
	\textit{F. Peng, R. A. Jacobs, M. A. Tanner} Bayesian inference in mixtures-of-experts and hierarchical mixtures-of-experts models with an application to speech recognition~// J. Amer. Stat. Assoc., vol. 91, no. 435, pp. 953–960, 1996.

\bibitem{Tuerk2001}
	\textit{A. Tuerk} The state based mixture of experts HMM with applications to the recognition of spontaneous speech~// Ph.D. thesis, Dept. Eng., Univ. Cambridge, Cambridge, U.K., 2001.

>>>>

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto .   
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{amsfonts}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

\title{Analysis of the properties of probabilistic models in learning problems with an expert\thanks{Grants or other notes
about the article that should go on the front page should be
placed here. General acknowledgments should be placed at the end of the article.}
}
\subtitle{}

%\titlerunning{Short form of title}        % if too long for running head

\author{Andrey V. Grabovoy        \and
            Alexandra I. Bazarova  \and
            Vadim V. Strijov
}

%\authorrunning{Short form of author list} % if too long for running head
\institute{
            Andrey V. Grabovoy\at Moscow Institute of Physics and Technology\\
              9 Institutskiy per., Dolgoprudny, Moscow Region, 141701, Russian Federation \\
              \email{grabovoy.av@phystech.edu}
           \and
           Alexandra I. Bazarova\at Moscow Institute of Physics and Technology\\
              9 Institutskiy per., Dolgoprudny, Moscow Region, 141701, Russian Federation \\
              \email{bazarova.ai@phystech.edu}
           \and
           Vadim V. Strijov \at Moscow Institute of Physics and Technology\\
              9 Institutskiy per., Dolgoprudny, Moscow Region, 141701, Russian Federation \\
              \email{strijov@phystech.edu}
}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}
This paper is devoted to the construction of interpretable models in machine learning. 
It solves the problem of approximating a given set of figures on a contour image.
Assumptions are introduced that the figures are curves of the second order.
When approximating figures, information about the type, location and form of curves, as well as the set of their possible transformations, is used.
Such information is called \textit{expert}, and the machine learning method based on expert information is called \textit {expert learning}.
It is assumed that the set of shapes is approximated by a set of \textit {local models}.
Each local model, based on expert information, approximates one shape in the contour image.
To build models, it is proposed to map second-order curves into a feature space where each local model is a linear model.
Thus, higher-order curves are recognized using the composition of linear models.
As an applied problem, the problem of approximating the iris of the eye on a contour image is considered.
\keywords{Mixture of experts \and Expert learning \and Linear models \and Interpretabe models}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

\section{Introduction}
\label{intro}
Interpretable model building in machine learning~\cite{Ribeiro2016} is one of the key challenges.
Modern solutions of the image classification problem based on deep learning networks ResNet, VGG, Intercept~\cite{Kaiming2015} are poorly interpreted models.
The papers~\cite{Han2020, Xingjun2019, Akhtar2018} show that deep learning networks are sensitive even to small noise in the data, which is due to their uninterpretability.

@@

This paper solves the problem of approximating second-order curves on a contour image. Second-order curves are selected for analysis, since they are easily described by linear models. In this case, these figures need to be restored in such applied problems as the problem of recognizing the iris of the eye~\cite{Matveev2010, Matveev2014, Bowyer2010}, the problem of describing the particle track in the hadron collider~\cite{Dalila2018}. Expert information about a second-order curve allows you to map points on a plane into a new feature description, where each curve is approximated by one linear model. A model that approximates one curve is called a \textit {local model}. To approximate the entire contour image, it is required to approximate several second-order curves using several local models. In this paper, the following restrictions on images are introduced:
\begin{enumerate}
	\item the image consists only of second-order curves;
	\item the image is approximated by a small number of second-order curves;
	\item the number and type of curves in the image is known.
\end{enumerate}

\begin{figure}[h!]
     \includegraphics[width=\textwidth]{figures/explanation}
     \caption {Example: a) expert information of the first expert; b) baseline data; c) expert information of the second expert}
    \label{intro:fig2}
\end{figure}

@@

\begin{figure}[h!]
	\subfloat[]{\includegraphics[height = 0.2\textheight]{figures/real_image}\label{intro:fig1:real}} 
	\subfloat[]{\includegraphics[height = 0.2\textheight]{figures/outline_image}\label{intro:fig1:outer}} 
\caption{An example of the image of the iris of the eye and its outline representation: a) the image of the iris of the eye; b) contour image of the iris and approximating the given image of the circumferences}
\label{intro:fig1}
\end{figure}

@@

\section{Statement of the problem of finding the parameters of the second-order curves in the image}
\label{sec:1}
Binary image is set:
$$ \mathbf{M} \in \{0, 1 \}^{m_1\times m_2},$$
where 1 corresponds to the black point of the image, and 0 corresponds to the white point of the background.
From the image $\mathbf {M} $, a sample$ \mathbf{C}$ is constructed, the elements of which are the coordinates $(x_i, y_i)$ of black points: $$\mathbf{C} \in \mathbb{R}^{N \times 2}. $$
The expert assumes that the image consists of a second-order curve~$\Omega$.
Let for a set of points $\mathbf {C} \in \mathbb {R}^{N \times 2} $ that form a curve $\Omega, $ expert information about the figure $E(\Omega) $is given.
The set $E (\Omega)$ consists of the shape $\Omega$ expected by the expert and the set of its admissible transformations. Based on the expert description, let us introduce mappings into a new problem for approximation:
\begin{equation}\label{eq1}
	K_{x}\bigl(E(\Omega)\bigr): \mathbb{R}^{2} \rightarrow \mathbb{R}^{n}, \quad K_{y}\bigl(E(\Omega)\bigr): \mathbb{R}^{2} \rightarrow \mathbb{R},
\end{equation} 
where~$K_{x}$ mapping objects to the attribute description of objects,~$n$is the number of features, and~$K_ {y}$ is a mapping to a target variable for an object. Applying the mappings~$K_ {x}, K_{y}$for the sample~$\mathbf {C}$ element by element we obtain:
\begin{equation}
\label{eq2}
	K_{x}\bigl(E(\Omega\bigr), \mathbf{c}) = \mathbf{x}, \quad  K_{y}\bigl(E(\Omega), \mathbf{c}\bigr) = y,
\end{equation}
where~$\mathbf{c} = (x_i, y_i)$ is a sample point $\mathbf{C}$.

@@

\section{Building an attribute description of figures}
\label{sec:3}
\paragraph{ Unified space for second-order curves.} An arbitrary second-order curve, the main axis of which is not parallel to the ordinate axis, is given by the following expression:
\[
\label{st:coef}
x^2 = B'xy+C'y^2+D'x+E'y+F',
\]
where the coefficients $B ', C'$ are subject to restrictions that depend on the type of the curve. The expression~\eqref{eq2} takes the following form:
\[
\label{st:K_map}
K_x\bigr(\mathbf{c}_i\bigr)=\left[x_iy_i, y_i^2, x_i, y_i, 1\right], \quad K_y\bigr(\mathbf{c}_i\bigr)=x_i^2,
\]
whence we obtain the linear regression problem for recovering the parameters~$ B ', C', D ', E', F '$ from the selected sample.

@@

\section{Composition of figures}
\label{sec:4}
o construct a composition of figures, we will use the expression~\eqref{9}, which takes the following form:
\begin{equation} 
\label{statment:optim:task}
\begin{aligned}
\mathcal{L} = \sum\limits_{\mathbf{c} \in \mathbf{C}} \sum\limits_{k = 1}^{K} \pi_k(\mathbf{c}, \mathbf{V})\left(K^{k}_y\bigr(\mathbf{c}\bigr) - \mathbf{w}_k^{\mathsf{T}}K^{k}_x\bigr(\mathbf{c}\bigr)\right)^2 + R\bigl(\mathbf{V}, \mathbf{W}, E(\Omega)\bigr) \rightarrow \min_{\mathbf{V}, \mathbf{W}},
\end{aligned}
\end{equation} 
where~$K^{k}_x, K^{k}_y$ expert representation of the~$k$-th expert. Assuming that all curves in the image are described by one attribute description $\mathbf {x} =K^{1}_x\bigr(\mathbf{c}\bigr)=\cdots=K^{K}_x\bigr(\mathbf{c}\bigr), x= K^{1}_y\bigr(\mathbf{c}\bigr)=\cdots=K^{K}_y\bigr(\mathbf{c}\bigr),$ we get the following optimization problem:
\begin{equation} 
\label{statment:optim:task:simp}
\begin{aligned}
\mathcal{L} = \sum\limits_{\left(\mathbf{x}, y\right) \in \mathfrak{D}} \sum\limits_{k = 1}^{K} \pi_k(\mathbf{x}, \mathbf{V})\left(y - \mathbf{w}_k^{\mathsf{T}}\mathbf{x}\right)^2 + R\bigl(\mathbf{V}, \mathbf{W}, E(\Omega)\bigr) \rightarrow \min_{\mathbf{V}, \mathbf{W}},
\end{aligned}
\end{equation}

@@

\section{Computing experiment}
\label{sec:5}

A computational experiment was carried out to analyze the quality of models of second-order curves in the image. The experiment is divided into several parts. The first part is an experiment with several circumferences in the image. The second part analyzes the convergence of the method depending on the noise level in the data and on the specified expert information. In the third part, an experiment is conducted to approximate the iris of the eye.

\subsection{ Experiment with circumstances }
\begin{figure}[h!]
	\subfloat[]{\includegraphics[height = 0.2\textheight]{figures/900.eps}} 
	\subfloat[]{\includegraphics[height = 0.2\textheight]{figures/901.eps}}
	\subfloat[]{\includegraphics[height = 0.2\textheight]{figures/902.eps}}

\caption{Multi-model depending on different prior assumptions and noise level. From left to right: circumferences without noise; noise in the radius of the circle; noise in the radius of a circle as well as arbitrary points throughout the image.}
\label{ce:fig3}
\end{figure}

\begin{figure}[h]
	\subfloat[]{\includegraphics[height = 0.2\textheight]{figures/900noise.eps}} 
	\subfloat[]{\includegraphics[height = 0.2\textheight]{figures/901noise.eps}}\\
	\subfloat[]{\includegraphics[height = 0.2\textheight]{figures/902noise.eps}}

\caption{Dependence of the parameters  $r$, $x_0$ and $y_0$ on the iteration number for different prior distributions. From left to right: circumferences without noise; noise in the radius of the circle; noise in the radius of a circle as well as arbitrary points throughout the image.}
\label{ce:fig4}
\end{figure}

@@

\subsection{ Experiment with different noise levels and variance of the prior distribution }
\begin{figure}[h!t]
\includegraphics[width=0.8\textwidth]{figures/beta_gamma}
\caption{ The result of the approximation for data with different noise levels~$\beta$ and on the variance of the prior distribution~$\gamma$}
\label{ce:fig6}
\end{figure}

@@

\subsection{Iris approximations }
\begin{figure}[h!]
	\subfloat[]{\includegraphics[height = 0.17\textheight]{figures/not_prior_real_example}} 
	\subfloat[]{\includegraphics[height = 0.17\textheight]{figures/prior_real_example}}
	\subfloat[]{\includegraphics[height = 0.17\textheight]{figures/prior_regular_real_example}} 
\caption{Visualization of the approximation of the iris: a) if the $ R_0 $ regularizer is specified; b) if the $ R_1 $ regularizer is specified; b) if the $ R_2 $ regularizer is specified}
\label{ce:fig6}
\end{figure}

\begin{figure}
     \includegraphics[width=\textwidth]{figures/experiment_real_not_prior}\\
     \caption{Visualization of the multi-model convergence process in the case of a regularizer~$R_0$}
    \label{ce:fig7}
\end{figure}

\begin{figure}
     \includegraphics[width=\textwidth]{figures/experiment_real_prior}
     \caption{Visualization of the multi-model convergence process in the case of a regularizer~$R_1$}
    \label{ce:fig8}
\end{figure}

\begin{figure}
     \includegraphics[width=\textwidth]{figures/experiment_real_regular}
     \caption{Visualization of the multi-model convergence process in the case of a regularizer~$R_2$}
    \label{ce:fig9}
\end{figure}

@@

\section{Conclusion}
\label{sec:6}
The paper proposes a method for constructing interpretable machine learning models based on expert information. The problem of approximation of the second-order curves: parabola, hyperbola, ellipse is considered as a problem. Approximation of curves of the second order is applied in the problem of approximation of the iris of the eye.

@@

%\begin{acknowledgements}
%If you'd like to thank anyone, place your comments here
%and remove the percent signs.
%\end{acknowledgements}

% Authors must disclose all relationships or interests that 
% could have direct or potential influence or impart bias on 
% the work: 
%
% \section*{Conflict of interest}
%
% The authors declare that they have no conflict of interest.

% BibTeX users please use one of
%\bibliographystyle{spbasic}      % basic style, author-year citations
%\bibliographystyle{spmpsci}      % mathematics and physical sciences
%\bibliographystyle{spphys}       % APS-like style for physics
%\bibliography{}   % name your BibTeX data base
